On affine extension of splint root systems

### 2013-02-01 AffineLieAlgebras/Splints/affine.tex
Minor changes

>>>>

\section{Branching coefficients, branching funcitons and characters}
\label{sec:branch-coeff-branch}

For affine Lie algebra $\gfh$ the specialized character can be computed as
\begin{equation}
  \label{eq:1}
  \mathrm{ch}_{\mu} (\tau, \{z^i \}) = \mathrm{tr}\left( e^{2\pi i \tau L_0
    +\frac{c}{24} - h_{\mu } + \sum_i z_i H^i_0} \right)= \mathrm{tr} \left(
  q^{L_0 +c/24-h_{\mu}} \prod_i \omega_i^{H^i_0}\right)
\end{equation}
Here $H^i$ are the elements of the Cartan subalgera of $\gf$, $q=e^{2\pi i
  \tau}$, $\omega_i = e^{2\pi i z_i}$, $h_{\mu} = \frac{(\mu,\mu+2\rho)}{2(k+h^{\vee}_{\gf})}$. 
Virasoro character for conformal family of primary field $\varphi_{\mu}$ for Wess-Zumino-Novikov-Witten model with affine Lie
algebra $\gfh$ is equal to restricted character multiplied by
$q^{h_{\mu}-c/24}$:
\begin{equation}
  \label{eq:2}
  \chi_{\mu} (\tau) = q^{h_{\mu}-c/24} \mathrm{ch} _\mu (\tau,0)
\end{equation}
